WSClean: an implementation of a fast, generic wide-field imager

### 2014-02-06 articles/2014/Article-WSClean/wsclean.tex
Article

For the WSClean time cost function $t_\textrm{WSClean}$ we find 
\begin{align}\label{eq:wsclean-computing-cost}
& t_\textrm{WSClean} (w_e,N_\textrm{Mvis},N_\textrm{freq},N_\textrm{kpix}) = \\ \notag%
& N_\textrm{chan} \left( 0.452 N_\textrm{kpix}^2 \log_2 N_\textrm{kpix} (w_e + 0.611) + 244 N_\textrm{Mvis} \right)
\end{align}
and for CASA we find
\begin{align}\label{eq:casa-computing-cost}
& t_\textrm{CASA}(w_e,N_\textrm{vis},N_\textrm{freq},N_\textrm{pix}) = \\ \notag%
& N_\textrm{chan} \left(1.03 N_\textrm{kpix}^2 \log_2 N_\textrm{kpix} + 5.93 N_\textrm{Mvis} (w_e + 1.71)^2\right) + 172.
\label{eq:casa-computing-cost}%
\end{align}
Parameter $w_e$ is the maximum $w$ value and is estimated with
\begin{equation}
 w_e = \frac{1}{\lambda}\left[\max |\mathbf{x}| \sin \textrm{ZA} + \max z \cos \textrm{ZA} \left(1.0 - \cos(\frac{1}{2}\textrm{FOV})\right)\right],
\end{equation}
where $\max |\mathbf{x}|$ is the maximum baseline length, $\max z$ is the maximum height difference between antennas and $\lambda$ is the wavelength.

>>>>

For the WSClean time cost function $t_\textrm{WSClean}$ we find 
\begin{align}\label{eq:wsclean-computing-cost}
& t_\textrm{WSClean} (w_e,N_\textrm{Mvis},N_\textrm{freq},N_\textrm{kpix}) = \\ \notag%
& N_\textrm{chan} \left( 0.452 N_\textrm{kpix}^2 \log_2 N_\textrm{kpix} (w_e + 0.611) + 244 N_\textrm{Mvis} \right)
\end{align}
and for CASA we find
\begin{align}\label{eq:casa-computing-cost}
& t_\textrm{CASA}(w_e,N_\textrm{vis},N_\textrm{freq},N_\textrm{pix}) = \\ \notag%
& N_\textrm{chan} \left(1.03 N_\textrm{kpix}^2 \log_2 N_\textrm{kpix} + 5.93 N_\textrm{Mvis} (w_e + 1.71)^2\right) + 172.
\label{eq:casa-computing-cost}%
\end{align}
Parameter $w_e$ is the maximum $w$ value and is estimated with
\begin{equation}
 w_e = \frac{1}{\lambda}\left[\max |\Delta \mathbf{x}| \sin \textrm{ZA} + \max \Delta z \cos \textrm{ZA} \left(1.0 - \cos(\frac{1}{2}\textrm{FOV})\right)\right],
\end{equation}
where $\max |\Delta \mathbf{x}|$ is the maximum baseline length, $\max \Delta z$ is the maximum height difference between antennas and $\lambda$ is the wavelength.

\begin{table*}
\begin{tabular}{lrrrrrrr}
 Survey   & $\lambda$ & FWHM  & Resolution & $\max |\Delta \mathbf{x}|$ & $\max \Delta z$ & int. time & B/$\delta \nu$ \\
\hline
 GLEAM    &           &       & 2'     & 2.9~km & 5~m & 2~s & 32~MHz/40~kHz\\
 EMU wide & 20 cm  & 1\degree & 10''    & 6~km &  0~m &     & ?/?\\
 MSSS low &  5 m   & 9.8\degree & 100'' & 5~km &      &10~s & 16~MHz/4~khZ\\
 MSSS high&  2 m   & 3.8\degree & 120'' & 5~km &      &10~s & 16~MHz/4~khZ\\
\end{tabular}
\end{table*}
